---
title: "The Toronto Annual Crime Report for 2020"
subtitle: "My subtitle if needed"
author: 
  - Bilal Haq
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence (broad and motivational). Second sentence (more specific about what you did and how). Third sentence (report findings). Fourth sentence (why all this matters)."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(knitr)
library(here)
```


# Introduction

First paragraph is motivational and broad (first sentence of abstract <- add water)

Second paragraph is about what was done and what was found (second and third sentence of abstract <- add water)

Third paragraph is about implications (take final sentence of abstract <- add water)

Final paragraph is about the remainder of this paper: i.e. Section \@ref(data) explains the data.

# Data

Paragraph introducing the dataset broadly. We obtain our dataset from the City of Toronto Open Data portal using the 'opendatatoronto' package [@citeopendatatoronto] and the statistical programming language R [@citeR].

Then show an extract of the dataset (Table \@ref(tab:dataextract)).

```{r dataextract, echo=FALSE, warning=FALSE, message=FALSE}
annual_reported_crimes <- 
  read_csv(here::here("inputs/data/annual_reported_crimes.csv"))

annual_reported_crimes |>
  filter(ReportedYear=="2020") |>
  select("GeoDivision", "Subtype", "Count_") |>
  slice(1:10) |>
  kable(
    caption="First 10 rows of dataset that shows frequency of crimes in 2020",
    col.names=c("Police Division", "Crime Type", "Count"),
    digits=1,
    booktabs=TRUE,
    linesep=""
  )
```

Paragraph or two more about Table \@ref(tab:dataextract).
- talk about how divisions in TPS work

We are interested in the relationship between the police division and the amount of crime that occurred there, because this measure can help the Toronto Police Service allocate their resources effectively, by focusing resources in particular divisions.
- paragraph focusing on central field commands (middle divisions) vs area field commands (outer divisions)

Figure X shows the relationship between the police division and the most popular crime that happens in that division.

```{r divisiongraph, echo=FALSE, warning=FALSE, message=FALSE}

annual_reported_crimes |>
  ggplot(aes(x=GeoDivision, 
             y=Count_, 
             color=Category)) +
  geom_point(alpha=0.8)
```



# References


